---
title: "{{PROJECT_NAME}}"
author: "{{ANALYST}}"
date: "`r Sys.Date()`"
date-format: long
format:
  html:
    output-file: preliminary_report.html
    theme: united
    title-block-banner: false
    grid:
      body-width: 900px
    toc: true
    toc-depth: 3
    toc-location: left
    toc-expand: true
    smooth-scroll: true
    code-fold: false
    fig-align: center
    fig-width: 6.5
    css: styleq.css
    tbl-colwidths: false
crossref:
  fig-title: "Figure"
  tbl-title: "Table"
csl: https://www.zotero.org/styles/apa
link-citations: true
editor: visual
---

```{r setup, echo=FALSE, include=FALSE}
library(knitr)
library(kableExtra)
library(scales)
library(ggplot2)
library(dplyr)
library(tidyr)
library(survival)
library(trcpetc)

knitr::opts_chunk$set(
  fig.align = "center",
  dev = "png",
  dev.args = list(pointsize = 11),
  fig.show = "hold",
  out.extra = 'style="border:20px solid white;"'
)

knit_hooks$set(
  inline = function(x) if (is.numeric(x)) round(x, 3) else x
)

options(knitr.kable.NA = "")
options(scipen = 999)
```

```{r example-data, echo=FALSE}
set.seed(123)

# load("../1_data/derived/2_descriptive.RData")

# Replace this example data with the results from 2_descriptive.R.
cars$study_id <- seq_len(nrow(cars))
cars$colour <- factor(ifelse(cars$speed > 10, "red", "blue"))

tab_overall <- trcpetc::table_one(cars)
tab_group <- trcpetc::table_one(cars, group = colour)
```

# Introduction

Quarto documents are very similar to Rmd documents. The advantage is that you get two editors that you can switch between in the toggle top left (Source vs. Visual). It can be convenient to use the Visual one, for example when 'hand-writing' a table. You can also access other formatting help in the task bar above.

Referencing literature works the same as in Rmd (brackets and at), for example [@Gao2026] .

| Abbreviation | Description         |
|--------------|---------------------|
| Rmd          | R-markdown document |
| Qmd          | Quarto document     |

: Table that has quickly been added using the "Table" toggle in the task bar

In this document, we also use the new trcpetc workflow for tables, i.e. table_one() to get the raw descriptives, then kable_table_one to automatically make the header nice etc.
## Background

## Objectives


# Methods

## Study population

## Data sources

## Outcomes

## Statistical analysis

Clinical characteristics were summarized using descriptive statistics. Continuous variables were characterized using median and interquartile range; dichotomous or polytomous variables were characterized using frequencies.

Between-group comparisons were evaluated using Wilcoxon rank-sum tests for continuous variables and Fisher's exact tests for dichotomous and polytomous variables.

Analyses were performed using `r R.version.string` (R Foundation for Statistical Computing, Vienna, Austria).



# Results

## Descriptive statistics

Use the descriptive results created in `2_descriptive.R` here.

See @tbl-cars-overall for an example of a referenced table.

```{r tbl-cars-overall, echo=FALSE}
#| tbl-cap: "Summary of overall characteristics"

kable_table_one(tab_overall)
```

```{r tbl-cars-group, echo=FALSE}
#| tbl-cap: "Summary of characteristics by colour"

kable_table_one(tab_group)
```

You can also include evaluated R expressions directly in prose when needed.

See @fig-cars for an example of a cross-referenced figure.

```{r fig-cars, echo=FALSE}
#| fig-cap: "Relationship between speed and distance"

plot(cars$speed, cars$dist)
```



# Discussion

# Conclusion